RB scheduling for different slices of eMBB and URLLC in the O-RAN system \vspace{-.1cm}

### 2022-03-31 Latex/journal_v2/version3/pr.tex
system model before change

\title{Network Slicing and Resource Allocation in an Open RAN System \vspace{-.1cm}
}
%
%\author{\IEEEauthorblockN{1\textsuperscript{st} Mojdeh Karbalaee Motalleb}
%\IEEEauthorblockA{\textit{Electrical and Computer Engineering} \\
%\textit{Tehran University}\\
%Tehran, Iran \\
%mojdeh.karbalaee@ut.ac.ir}
%\and
%\IEEEauthorblockN{2\textsuperscript{nd} Vahid Shah-Mansouri}
%\IEEEauthorblockA{\textit{Electrical and Computer Engineering} \\
%\textit{Tehran University}\\
%Tehran, Iran \\
%vmansouri@ut.ac.ir}
%\and
%\IEEEauthorblockN{3\textsuperscript{rd} Salar Nouri Naghadeh}
%\IEEEauthorblockA{\textit{Electrical and Computer Engineering} \\
%\textit{Tehran University}\\
%Tehran, Iran \\
%salar.nouri@ut.ac.ir}
%}
%%%%%  \author{
%%%%%    \IEEEauthorblockN{Mojdeh Karbalaee Motalleb}
%%%%%    \IEEEauthorblockA{School of ECE, College of Engineering, University of Tehran, Iran \\
%%%%%    Email: \{mojdeh.karbalaee\}@ut.ac.ir,
%%%%%    \vspace{-.2cm}
%%%%%  }
%%%%%  }

@@

\section{System Model and Problem Formulation}
\subsection{System Model}
%This paper deals with the challenges of heterogeneous vehicular and cellular networks.
Assume we have two preallocated slices serving two services, eMBB, and URLLC services; 
eMBB Service consists of $U_{1}$ single-antenna user equipments (UEs) and URLLC service consists of $U_2$ UEs.
Assume our system consists of $K$, preallocated physical resource blocks (PRBs). Moreover, the system considers to have $M_s^{d}$ VNFs for the processing of O-DU, $M_s^{c}$ VNFs for the processing of O-CU-UP of eMBB and URLLC ($ s \in \{1, 2\}$). 
Virtual network functions (VNFs) are functional blocks of the system. Each VNF instance runs on a virtual machine (VM) using resources from the data centers. 
Moreover, we assume there is a cell with one multi-antenna O-RU that serves UEs.
\subsection{The Achievable Rate}
The eMBB services typically use more than a one-time slot. But URLLC services use part of a time slot (mini-slot) since it has short packet transmission. In addition, the URLLC must be punctured as soon as it has requested service as it requires very low latency.

%The SNR of $i^{th}$ UE requesting served at slice $ss \in \{1, 2\}$ is obtained from
%\begin{equation}\label{eq2}
%\rho_{u(s,i)} =  \frac{\sum_{k=1}^{K_{s}}e_{u(s,i)}^k p_{u(s,i)}^{k}|{\bold{h}_{R,u(s,i)}^{H \: k}}|^2}{BN_0},
%\end{equation} 
%where $p_{u(s,i)}^{k}$ represents the transmission power allocated by O-RUs to $i^{th}$ UE served at slice $s$ on PRB $k$.
%${\bold{h}_{R,u(s,i)}^{k}} \in \mathbb{C}^{R}$ is the vector of channel gain of a wireless link from 
%O-RUs to the $i^{th}$ UE in $s^{th}$ slice. 
%Moreover, $e_{u(s,i)}^k \in \{0,1\}$ is a binary variable that illustrates whether PRB $k$ is assigned to the $i^{th}$ UE allocated to $s^{th}$ slice or not. 
%Also, $BN_0$ denotes the power of Gaussian additive noise.
%Moreover, we assume that each PRB is assigned to no more than one UEs. So we have
%\begin{equation}
%\sum_{s=1}^S \sum_{u=1}^{U_s} e_{u(s,i)}^k = 1
%\end{equation} 
The achievable data rate for the $i^{th}$ UE request eMBB slice can be written as $\mathcal{R}_{i}^{e}(t)$.
\begin{equation}\label{eq1}
\mathcal{R}_{i}^e(t) = \sum_{k = 1}^K e^k_i(t) B (1-\frac{n^k_i(t)}{S}) \log_2({1+\frac{p^k_i(t)h^k_i(t)}{B \times N_0}}),
\end{equation}
where $B$ is the bandwidth of RBs. Also, $B\times N_0$ denotes the power of Gaussian additive noise. 
Moreover, $e^k_i(t)\in \{0,1\}$ is a binary variable that illustrates whether PRB $k$ is assigned to the $i^{th}$ eMBB UE or not. 
$p^k_i(t)$ represents the transmission power allocated by O-RU to $i^{th}$ UE of eMBB using PRB $k$.
$h^k_i(t)$ is the channel gain of a wireless link from 
O-RU to the $i^{th}$ eMBB UE using $k^{th}$ PRB. In addition, $S$ is the total number of mini-slots of a PRB. 
Furthermore, $n^k_i(t)$ is the number of URLLC punctured slots.

>>>>

\title{RB scheduling for different slices of eMBB and URLLC in the O-RAN system \vspace{-.1cm}
}
%
%\author{\IEEEauthorblockN{1\textsuperscript{st} Mojdeh Karbalaee Motalleb}
%\IEEEauthorblockA{\textit{Electrical and Computer Engineering} \\
%\textit{Tehran University}\\
%Tehran, Iran \\
%mojdeh.karbalaee@ut.ac.ir}
%\and
%\IEEEauthorblockN{2\textsuperscript{nd} Vahid Shah-Mansouri}
%\IEEEauthorblockA{\textit{Electrical and Computer Engineering} \\
%\textit{Tehran University}\\
%Tehran, Iran \\
%vmansouri@ut.ac.ir}
%\and
%\IEEEauthorblockN{3\textsuperscript{rd} Salar Nouri Naghadeh}
%\IEEEauthorblockA{\textit{Electrical and Computer Engineering} \\
%\textit{Tehran University}\\
%Tehran, Iran \\
%salar.nouri@ut.ac.ir}
%}
%%%%%  \author{
%%%%%    \IEEEauthorblockN{Mojdeh Karbalaee Motalleb}
%%%%%    \IEEEauthorblockA{School of ECE, College of Engineering, University of Tehran, Iran \\
%%%%%    Email: \{mojdeh.karbalaee\}@ut.ac.ir,
%%%%%    \vspace{-.2cm}
%%%%%  }
%%%%%  }

@@

\section{System Model and Problem Formulation}
\subsection{System Model}
%This paper deals with the challenges of heterogeneous vehicular and cellular networks.
Assume we have two preallocated slices serving two services, eMBB, and URLLC services; 
eMBB Service consists of $U_{1}$ single-antenna user equipments (UEs) and URLLC service consists of $U_2$ UEs.
Assume our system consists of $K$, preallocated physical resource blocks (PRBs). Moreover, the system considers to have $M_s^{d}$ VNFs for the processing of O-DU, $M_s^{c}$ VNFs for the processing of O-CU-UP of eMBB and URLLC ($ s \in \{1, 2\}$). 
Virtual network functions (VNFs) are functional blocks of the system. Each VNF instance runs on a virtual machine (VM) using resources from the data centers. 
Moreover, we assume there is a cell with one multi-antenna O-RU that serves UEs.
\subsection{The Achievable Rate}
The eMBB services typically use more than a one-time slot. But URLLC services use part of a time slot (mini-slot) since it has short packet transmission. In addition, the URLLC must be punctured as soon as it has requested service as it requires very low latency.
Our current work allocates RBs to eMBB users at the beginning of each time slot using the PF principle, a scheduling strategy that balances throughput with fairness \cite{shi2022risk}.

The achievable data rate for the $i^{th}$ UE request eMBB slice can be written as $\mathcal{R}_{i}^{e}(t)$.
\begin{equation}\label{eq1}
\mathcal{R}_{i}^e(t) = \sum_{k = 1}^K e^k_i(t) B (1-\frac{n^k_i(t)}{S}) \log_2({1+\frac{p^k_i(t)h^k_i(t)}{B \times N_0}}),
\end{equation}
where $B$ is the bandwidth of RBs. Also, $B\times N_0$ denotes the power of Gaussian additive noise. 
Moreover, $e^k_i(t)\in \{0,1\}$ is a binary variable that illustrates whether PRB $k$ is assigned to the $i^{th}$ eMBB UE or not. 
$p^k_i(t)$ represents the transmission power allocated by O-RU to $i^{th}$ UE of eMBB using PRB $k$.
$h^k_i(t)$ is the channel gain of a wireless link from 
O-RU to the $i^{th}$ eMBB UE using $k^{th}$ PRB. In addition, $S$ is the total number of mini-slots of a PRB. 
Furthermore, $n^k_i(t)$ is the number of URLLC punctured slots that is denoted as follow,
\begin{equation}
n^k_i(t) = \sum_{j=1}^{U_2}{\zeta}_j(t)\tau \mathfrak{N} 
\end{equation}
